Exploring Disparate Data: Part 1

### 2024-11-03 A3-Pt1.Rmd
Update A3-Pt1.Rmd

cyclones_data <- cyclones_data_update_2 |>
    mutate(
        category = ordered(
            case_when(
                # YOUR CODE HERE
            ),
            levels = cat_levels
        )
    )

@@

```{r}
# YOUR CODE HERE
```

>>>>

cyclones_data <- cyclones_data_update_2 |>
    mutate(
        category = ordered(
            case_when(
                # YOUR CODE HERE
                max_wind < 34 ~ "TD",
                max_wind >= 34 & max_wind < 64 ~ "TS",
                max_wind >= 64 & max_wind < 83 ~ "1",
                max_wind >= 83 & max_wind < 96 ~ "2",
                max_wind >= 96 & max_wind < 113 ~ "3",
                max_wind >= 113 & max_wind < 137 ~ "4",
                max_wind >= 137 ~ "5"

            ),
            levels = cat_levels
        )
    )

@@

```{r}
# YOUR CODE HERE
write_parquet(cyclones_data, "cyclones_data.parquet")
```
